\documentclass[a4paper,12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}

\title{\textbf{VideoTube Frontend Architecture & Implementation Plan}}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Overview}
A modern, highly-scalable React frontend consuming the VideoTube backend APIs, utilizing Tailwind CSS, Redux Toolkit, and React Router.

\section*{Phase 1: Foundation & Dependencies}
\begin{enumerate}[label=\arabic*.]
\item Initialize core routing and state tools: \texttt{react-router-dom}, \texttt{@reduxjs/toolkit}, \texttt{react-redux}.
\item Configure Tailwind CSS: \texttt{tailwindcss}, \texttt{postcss}, \texttt{autoprefixer}.
\item Set up Axios for data fetching with a custom instance and interceptors for JWT handling.
\item Optional: Rename \texttt{componants/} to \texttt{components/}. Create \texttt{hooks/} and \texttt{utils/}.
\end{enumerate}

\section*{Phase 2: Core Configuration}
\begin{enumerate}[label=\arabic*.]
\item Set up Redux store in \texttt{src/store/store.js}.
\item Create \texttt{authSlice} to manage global user state.
\item Configure environment variables in \texttt{.env} and map them in \texttt{src/conf/config.js}.
\end{enumerate}

\section*{Phase 3: Routing & Layouts}
\begin{enumerate}[label=\arabic*.]
\item Define routing using \texttt{createBrowserRouter} or \texttt{<Routes>}.
\item Build \texttt{AppLayout} with Header, Sidebar, and \texttt{<Outlet />}.
\item Create \texttt{AuthLayout} for protected routing.
\end{enumerate}

\section*{Phase 4: Component Construction}
\begin{enumerate}[label=\arabic*.]
\item Build reusable UI components: Button, Input, Logo, VideoCard, Loader, Avatar.
\item Build authentication components: Login Form and Registration Form.
\end{enumerate}

\section*{Phase 5: Page Implementation}
\begin{enumerate}[label=\arabic*.]
\item Home Page: Fetch all videos with pagination or infinite scroll.
\item Authentication Pages: Login and Signup.
\item Video Detail Page: Video player, metadata, like/subscribe buttons, comments.
\item Channel Profile Page: User info, subscribers, uploaded videos.
\item Dashboard: Creator tools and channel stats.
\item Interaction Pages: Liked videos, history, playlists.
\end{enumerate}

\section*{Relevant Files}
\begin{itemize}
\item \texttt{frontend/package.json} — dependencies.
\item \texttt{frontend/src/store} — Redux setup.
\item \texttt{frontend/src/conf} — API configuration.
\end{itemize}

\section*{Verification}
\begin{enumerate}
\item Axios interceptors refresh token on 401 errors.
\item Protected routes redirect unauthenticated users.
\item Environment variables resolve correct backend URL.
\end{enumerate}

\section*{Decisions}
\begin{itemize}
\item Redux for authentication state.
\item API fetching handled locally with \texttt{useEffect}.
\item Persistent Sidebar and Header layout.
\end{itemize}

\section*{Further Considerations}
\begin{enumerate}
\item File uploads using \texttt{FormData} for avatar, cover image, and video.
\item Consider using data table libraries like \texttt{react-table} or \texttt{ag-grid}.
\end{enumerate}

\end{document}
